\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{Sherpur, the name of exquisite beauty}
\author{M Riazul Islam}
\date{31 December 2023}

\begin{document}

\maketitle
\tableofcontents
\break

\section{Preface}
I started writing this script on the 31st night of 2023, hearing the flame and fireworks sound which a hated. I want to do something like journaling the resolution of the year or a gratification journal. Interesting Fact: When I sat on a chair to write this script was 2023, I stood up from my chair in 2024. During this time I with my mother exchanged New Year wishes with my father via video call.

\section{Introduction}

When I started school I was timid as well as introverted but when the day I completed my classes and preparing for SSC now I am the founding president of the Victorian Debating Club. Not only have I not participated in any major recitation competitions or won awards, but I got many awards from my school for participating in those competitions which I used to neglect or hate.

\section{Gratitude}

I have been awarded the Best Student award in Nation Education Week 2023 for Sherpur District, which is one of the most crucial accolades in my life, and I treat it as a school-ending gift for myself.
I feel gratitude to all of my teachers, friends, relatives, well-wishers, and mostly to my parents.

\section{Starting}

I started my journey to this school in 2019. A new boy from Jashore who didn't know what next to do in his life got his uncle My choto Chacchu as a roommate who was also a student of the same alma mater. Interestingly My father also has passed his secondary education from this school. That was another reason to choose this school for me.

\section{School}
I was involved in most of the extracurricular events. 

\section{Friends} 

I got my cousin as a classmate-Mahid, who was my first peer to share different thoughts, I've learned a lot as a beginner at computer stuff from him. We discussed science, tech related topics. Even our bond has been stronger since then.
Jisan, Science-Geek, my first Benchmate, discussed a lot of scientific thoughts in the Tiffin period. I spent most of the time during school with Sohail, Nishar, and Jawad. I miss them now I can realize how they were encouraging and enjoyable to me Rahat- always used to make laugh me, he named me Wikipedia 2.0 which was very funny. Schoccho Babu, Tasin, Mahim, Tushar, Fahim, and Siam, were my funmates. Adnan is one of my astronomy geek friends. Arnob and Noman are a movie geek. Adib and Nohan are the names of gifted boys from whom I learned a lot. Anirban, Nuhin, Sagor, Sneho, Apurbo, and Swapnil are my beloved juniors and founding members of the Victorian Debating Club with whom I worked.



\section{Teachers} I am grateful for these extraordinary teachers I was introduced within Sherpur:
Debate Mentor Shahidul Islam, Fahmida Mam, Shamimul Haque Sir, Nazrul Islam Sir, Imrul Sir, Anis Sir, Anwer Sir, Rahim Sir, Zubair Sayed Sir, Rezwan Sir. Rakib Hasan Sir, Salam Sir


\section{Public Library} 
I spent the second most time after school reading books from the public library Sherpur. I borrowed countless books and finished reading comics, papers, and books in the library. I spent my academic self-study in this library. I saw many brothers and uncles preparing for their desired jobs or exams. I feel good when I see them getting accepted their desired destination. I've participated in many competitions from 2019 to 2023 on-site events and got the best reader accolade on National Library Day 2023 Librarian sir, Sazzadul Karim is a name of inspiration, He said to me 'Books are also food, but they are for our mind, we have to read and write more'. Not only did he inspire me with books but also gave suggestions for our debate club and debate events. I have tears in my eyes while writing it as my library card expiry date is expired but the hearty love for this incident is crying.

\section{Visiting Sites} 
I've visited Gajni Abakash, the name of Green Beauty. I spent some valuable hours with my cousins exploring the beautiful site. I pondered some geological things there. Hillock/knoll of Gajni was cool as I saw it for the first time in my life. We explored Gajni from a watchtower with binoculars. I used to cricket matches in the Stadium of Shepur. It was reconstructed when I came to Sherpur Earlier

\section{Culture} 
Sherpur is the most culturally very rich district I've ever seen, I got exposure to some beautiful cultural minds. Shib Shankar Karua Sir, Associate Lecturer of Sherpur Govt College, may be absent nowhere where the cultural event is reoccurring. I've learned a lot from him. Sahila Akter, then Deputy Commissioner worked very hard to get recognition of Tulshimala Rice as a GI product for Sherpur and Successfully Done. Harunur Rashid, my former Head teacher as well as an art teacher, is one of the prominent sculptors in Bangladesh, made some extraordinary sculptures, and statues around the world. He was a Fine Arts Student at DU, who then studied Sculpture in Japan. ATM Ziaul Islam, Sub-Secretary of now Bangladesh, and former ADC of Sherpur is the most talented cultural mind I've ever seen. 


\section{Victorian Debating Club} 
The debate was a rich culture in Sherpur, but not at my period in my school. I have a dream after watching BTV debate events on YouTube, to be a debater. Because of the pandemic, it wouldn't be possible. Later on, I get a chance to participate in debate events from school. But there existed no debate activities at my school. From this concern, with the very crucial help of my headmaster, and some eloquent-minded juniors and peers I founded the Victorian Debating Club. We struggled a lot at first attempts of participation in district events containing zero prior experience. I can remember the day I competed first debate, my hand and legs shivered in front of the FOR team and judges. What an embarrassing moment it was in my life! But That was a slingshot event in my life I believe. We worked hard to improve our debate as well as club members. In a few months, we had outstanding success in the event. At last, we made our teachers feel proud. I got a chance to represent our club and school at the national level as well. It wouldn't be possible without the help of teachers. We got awards at the District level, divisional, and national education week also. Most importantly we made friends and collaboration with Mymensingh Zilla School and Jashore Zilla School Debating Club members. We have been sharing a lot of magnificent experiences.

\section{Organizations} Shahin DOHPS
Department of ICT office, Sherpur supported with not only technical but also giving valuable suggestions. They helped me to represent my project in national Competitions. I will be very grateful to them

\section{First Writing} 
I put pen to paper in Sherpur at first when I was a 6th grader in a hostel with my uncle. I wrote several poetries after getting inspiration from the books I got prizes from school. I used to show my writings to my uncle and cousins. They appreciated it. and truly I got motivation from them. Almost 10+ poetry I've written. Most of them I've published online, and some are published in my school's weekly magazine, monthly, and kids' magazines. I wrote Tika Kahini- Covid Vaccination Experience Essay. Now Writing is my passion.





\end{document}
